% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true,
  linkcolor=blue,   % color of internal links
  citecolor=blue,   % color of links to bibliography
  urlcolor=blue,    % color of external links
  pagebackref=true,
  implicit=false,
  bookmarks=true,
  bookmarksopen=true,
  pdfdisplaydoctitle=true
}

% the margin option causes section titles to appear to the left of body text 
\textwidth=5.75in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Matthew R. Goodman } % the \\[12pt] adds a blank line after name
 
\address{{\bf Home Address} \\ 1473 Oak Street \\ San Francisco, CA 94117 \\
         (562) 546-3326 \\ meawoppl@gmail.com \\ www.craneium.net}
\address{{\bf Work Address} \\ 1087 Mission St \\ San Francisco, CA 94103 \\  
         (520) 591-5245  \\ matt@3scan.com \\ www.3scan.com}

\begin{resume} 
 
\section{Objective} 
Complete the BME PhD.~program at UT Austin while working with 3Scan to
commercialize knife-edge scanning microscopy.

\section{Education} 
PhD. Biomedical Engineering (Projected completion Spring 2017) \\
University of Texas at Austin

M.S. Materials Science and Engineering, 
(GPA 3.83/4.0) \\
Thesis: ``Properties of Stochastic Flow and Permeability of Random Porous Media'' 
  (\href{http://hdl.handle.net/10150/193422}{link})  \\
University of Arizona, Tucson, AZ 

B.S. in Materials Science and Engineering (In major GPA 3.55/4.0) \\
University of Arizona, Tucson, AZ 

\section{Publications}
  C Sung, Y Choe, M Goodman, T Huffman, 
  ``Scalable, Incremental Learning for Cell Detection in High-Throughput 3D Microscopy Data''
  IJCNN 2013.

  AG Hendrick, RG Erdmann, MR Goodman, 
  ``Practical Considerations for Selection of Representative
  Elementary Volumes for Fluid Permeability in Fibrous
  Porous Media,'' Transport in Porous Media.  Volume 94.  2012. 
  (\href{http://dx.doi.org/10.1007/s11242-012-0051-8}{link})

  MR Goodman. ``Brain--Machine Interfaces'' -- Chapter 26 of \textit{New Materials and Technologies For Healthcare.} ISBN: 978-1848165588. 2012.
  (\href{http://amzn.com/1848165587}{link})

  RG~Erdmann, AG~Hendrick, and MR~Goodman
  ``Properties of Stochastic Permeability,'' 
  Transactions of the Indian Institute of Metals. 2011. 
  (\href{http://dx.doi.org/10.1007/s12666-009-0038-5}{link})

\section{Experience}
{\bf Co-Founder and Lead Software Architect,} 3Scan \hfill 
June 2011 -- Present
\begin{itemize}  \itemsep -2pt 
\item Architected complete microscopy tool suite including image processing 
  (acquisition, compression, and visualization), 
  precision stage automation, and control system optimization.
\item Designed and implemented precompression filter in CUDA for high-speed data processing. 
\item Co-wrote successful grant to StartupChile.  Lead performer on
  DARPA contract.   Designed web based microscope/sample/data management server with WebGL and Meteor.
\end{itemize}

{\bf Graduate Researcher,} University of Texas at Austin \hfill 
Fall 2010 -- Present
\begin{itemize} \itemsep -2pt 
\item Computational modeling and imaging analysis of the primary visual cortex of primates
\item Development of machine learning techniques for medical recommendation systems
\end{itemize}
{\bf Graduate Research Assistant,} University of Arizona \hfill
Fall 2008 -- Spring 2010
\begin{itemize} \itemsep -2pt 
\item Modeled heat and mass transfer for NASA/ESA space solidification experiments on ISS.
\item Developed HPC CFD solver for solidification, microfluidics, and biological systems.
\end{itemize}

{\bf Consultant,} PACE Metallography, ATI Allvac, Phoenix Heat Treating, \hfill Various

{\bf Scientific Data Analyst,} ATI Allvac, Monroe, NC \hfill
Summer 2007 and Summer 2008
\begin{itemize} \itemsep -2pt 
\item Unified huge body of process data from several databases for purposes of 
  process auditing and improvement by data--mining and machine--learning techniques
\item Developed algorithms used by engineers and business analysts for understanding 
  complex processes resulting in large cost savings by predictive/preventive maintenance  
% \item Automated post process
%   simulation of complex solidification phenomena for purposes of
%   statistical process control and improvement (Python)
\item Data--mining and scientific data analysis for process control resulting
  in process improvement and sizable cost savings
\end{itemize}

{\bf MSE Laboratory TA/Preceptor,} University of Arizona \hfill Fall 2007 -- Spring 2008
\begin{itemize} \itemsep -2pt 
\item MSE 414 -- Solidification of Castings -- Ran aluminum casting laboratory 
\item MSE 223L -- Materials Processing -- Taught three groups of 5--7
  about materials processing
\item MSE 110 -- Solid State Chemistry -- Oversaw MSE related lab
  activities
\end{itemize}

\section{Leadership} 
{\bf Project Leader,}  SEDS ``Rockoon''  project \hfill   Fall 2008 -- Spring 2010
\begin{itemize} \itemsep -2pt
\item Led team of two--dozen undergraduates in interdisciplinary design project
\item Responsible for FAA Clearances and safety of high-altitude high-power rocketry 
\end{itemize}

{\bf President,} Keramos \& {\bf Vice--President,} Material Advantage  \hfill  Fall 2007 -- Spring 2008

\begin{itemize} \itemsep -2pt
\item MSE Honors Fraternity and MSE Tutoring and Social Organization -- Lead ~10 students in outreach,
  teaching, and grant-writing. Keramos Awarded ``Most Improved Chapter''  
\end{itemize}

{\bf Treasurer,} h+ Tucson \hfill Fall 2007 -- Spring 2008
\begin{itemize} \itemsep -2pt
\item Technoprogressive Journal Club -- Basis of ``h+ magazine''
\end{itemize}

\section{Academic Honors} 
UT -- NIH NRSA Fellowship for Imaging Science and Informatics (2010)\\
UA -- Dean’s List (Spring 2008) \\
UA -- ASM International -- Darko Babic Scholarship (2007--2008) \\
UA -- ASM National Education Subcommittee Student Representative (2007--2008) \\
UA -- College of Engineering -- Award for Academic Distinction (2006--2008) \\
UA -- College of Engineering -- Departmental Honors for Outstanding Achievement (2005--2006)

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computational Skills}
   \begin{tabular}{l p{5.5in}}
    \underline{Languages:} & Python (numpy/scipy etc), C/C++/CUDA, m, \LaTeX  \\
    \underline{Software:}  & *nix environments, CFD and HT (FD, FEM, SPH) \\
    \underline{Web:}       & www.craneium.net (rails, WebGL, joomla! html, php, sql)
 \end{tabular}

\section{Activities and Interests}
Brain-Machine Interfaces; Spelunking; Rock Climbing; Japanese; 
Computational Linguistics; Visualization and Perception; Blacksmithing and Casting
\end{resume} 
\end{document}